---
title: "Pod work"
author: "Mike Cecil"
date: "2023-07-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Quality check

This script performs the following processing steps
- Images for each site of raw Mark observations, curve-fit, and LSP dates are exported to a .pdf file, 'pod_pheno_extract_qual_trs.pdf'.
- A table for quality check is exported to 'all_sites_quality_check_trs_BEFORE.csv', with columns for checking each LSP date, e.g. "G_keep" for greenup.
- Using the .pdf file, the user checks the Mark LSP dates for each site, and updates the table in the .csv file, using TRUE to keep the site's LSP date and FALSE to remove it from consideration. After finishing all sites, the user updates the column names from "G_keep" to "G_keep_post" etc, and renames the file 'all_sites_quality_check_trs_AFTER.csv'. 
- The 'all_sites_quality_check_trs_AFTER.csv' file is read in 'analysis_MULTISENSOR.Rmd' and all LSP dates recorded as FALSE in "G_keep_post" etc. have their dates set to NA.  



```{r}
library(dplyr)
#library(randomForest)
library(tidyr)
library(ggplot2)
library(stringr)
library(lubridate)
library(Rcpp)
library(phenofit)
library(zoo)
library(here)
library(terra)
library(scorepeak)
library(ranger)
library(pspline)

```

```{r}

fit_var <- function(df, colName, lambda, w_colName = NA, weights = F, quality_band = F){
 
  # mask out bad pixels if quality band option is True
  if (quality_band == T){
    df[ (!is.na(df$quality_band)) & df$quality_band != 'good', colName] <- NA
  }
  
  fitted_vi_col_name <- paste0(colName, "_fitted")
  y_all <- df[[colName]] 
  #  print(y_all)
  y_all[is.infinite(y_all)] <- -9999
  y_all[is.na(y_all)] <- -9999
  if(weights == T ){
    w <- df[[w_colName]]
  } else {
    w <- (y_all != -9999)
  }
  y_whit <- whit2(y_all, lambda, w)
  #  print(y_whit)
  df[[fitted_vi_col_name]] <- y_whit
  return(df)
}


plot_quality <- function(df, 
                         vi_col,
                         vi_col_fitted,
                         g_qual,
                         m_qual,
                         s_qual,
                         d_qual){
  
  
  df[['ndvi_pad']] <- df[[vi_col]]
  df[['ndvi_pad_fitted']] <- df[[vi_col_fitted]]

  
  max_vi <- max(df$ndvi_pad_fitted, na.rm = T)
  # ## Beck fit
  ndvi_col <- 'ndvi_pad_fitted'
  finefit_mark <- FitDL.Beck(df[[ndvi_col]])
  models_mark <- curvefit(df[[ndvi_col]], methods = 'Beck')
  dates_indices_mark_15 <- PhenoTrs(models_mark$model$Beck, IsPlot = F,
                                 trs = c(0.15))
  dates_indices_mark_90 <- PhenoTrs(models_mark$model$Beck, IsPlot = F,
                                 trs = c(0.90))
  dates_indices_mark <- c(dates_indices_mark_15[1], 
                          dates_indices_mark_90[1],
                          dates_indices_mark_90[2],
                          dates_indices_mark_15[2])
  dates_mark <- df$date[dates_indices_mark]
  dates_collapse_mark <- dates_mark %>% as.character() %>% paste(collapse = ' ')
  ndvi_beck <- finefit_mark$zs$iter2
  df$ndvi_beck <- ndvi_beck
  

  colors <- c(`good` = 'green',
             `maybe` = 'yellow4',
             `no` = 'red')
  
  
 # print(finefit_mark)
#  print(models_mark)
 # print(ndvi_beck)
  p <- ggplot(df) +
  #  geom_point(aes(x = date, y = ndvi_pad), col = 'green') +
  #  geom_point(aes(x = date, y = ndvi_pad), col = 'red', alpha = 0.5) +
  #  geom_point(aes(x = date, y = ndvi_pad, col = quality_band), alpha = 0.5) +
    scale_color_manual(values = colors) +

    geom_line(aes(x = date, y = ndvi_pad_fitted), alpha = 0.5) +
    geom_line(aes(x = date, y = ndvi_beck), col = 'blue') +
    geom_point(aes(x = date, y = ndvi_pad), col = 'red', alpha = 0.5) +
    theme_bw() +
    ylim(0, (1.1 * max_vi) ) + 
    ylab(vi_col) +
    geom_vline(xintercept= dates_mark[1], linetype= `g_qual`, lwd= 2, color = "lightgreen") +
    geom_vline(xintercept= dates_mark[2], linetype= `m_qual`, lwd= 2,  color = "darkgreen") +
    geom_vline(xintercept= dates_mark[3], linetype= `s_qual`, lwd= 2,  color = "yellow2") +
    geom_vline(xintercept= dates_mark[4], linetype= `d_qual`, lwd= 2,  color = "orange3") +
  #  geom_vline(xintercept = maxima_dates, linetype = 'solid', color = 'orange', lwd = 2) +
 #   geom_vline(xintercept = minima_dates, linetype = 'solid', color = 'purple', lwd = 2) +
    
    ggtitle(paste0(location, ' ', dates_collapse_mark))
#  plot(p)
#  print(p)
 # return(finefit_mark)
  return(list(p, dates_mark))
  
}




 
```

```{r}
load(file = here('data/all_sites_post_mgmt.rda'))
load(file = here('data/data_post_VIIRS_sr_fit.rda'))
```




## Quality of obs

```{r}

#sites <- all_sites$Location

all_sites$evi2_G_trs_delta <- sapply(1:nrow(all_sites), function(x){
  current_lsp <- all_sites$evi2_G_trs[x] %>% as_date()
  current_site <- all_sites$Location[x]
  current_df <- data %>% filter(Location == current_site)
  current_df_filt <- current_df %>% filter(!is.na(evi2))
  a <- min(abs(current_df_filt$date - current_lsp) ) %>% as.numeric()
})

all_sites$evi2_M_trs_delta <- sapply(1:nrow(all_sites), function(x){
  current_lsp <- all_sites$evi2_M_trs[x] %>% as_date()
  current_site <- all_sites$Location[x]
  current_df <- data %>% filter(Location == current_site)
  current_df_filt <- current_df %>% filter(!is.na(evi2))
  a <- min(abs(current_df_filt$date - current_lsp) ) %>% as.numeric()
})

all_sites$evi2_S_trs_delta <- sapply(1:nrow(all_sites), function(x){
  current_lsp <- all_sites$evi2_S_trs[x] %>% as_date()
  current_site <- all_sites$Location[x]
  current_df <- data %>% filter(Location == current_site)
  current_df_filt <- current_df %>% filter(!is.na(evi2))
  a <- min(abs(current_df_filt$date - current_lsp) ) %>% as.numeric()
})

all_sites$evi2_D_trs_delta <- sapply(1:nrow(all_sites), function(x){
  current_lsp <- all_sites$evi2_D_trs[x] %>% as_date()
  current_site <- all_sites$Location[x]
  current_df <- data %>% filter(Location == current_site)
  current_df_filt <- current_df %>% filter(!is.na(evi2))
  a <- min(abs(current_df_filt$date - current_lsp) ) %>% as.numeric()
})

all_sites$evi2_G_trs_hq <- sapply(1:nrow(all_sites), function(x){
  current_lsp <- all_sites$evi2_G_trs[x] %>% as_date()
  current_site <- all_sites$Location[x]
  current_df <- data %>% filter(Location == current_site)
  current_df_filt <- current_df %>% filter(!is.na(evi2)) %>% filter(abs((date - current_lsp) %>% as.numeric()) <= 5 ) 
  a <- nrow(current_df_filt)
})

all_sites$evi2_M_trs_hq <- sapply(1:nrow(all_sites), function(x){
  current_lsp <- all_sites$evi2_M_trs[x] %>% as_date()
  current_site <- all_sites$Location[x]
  current_df <- data %>% filter(Location == current_site)
  current_df_filt <- current_df %>% filter(!is.na(evi2)) %>% filter(abs((date - current_lsp) %>% as.numeric()) <= 5 ) 
  a <- nrow(current_df_filt)
})

all_sites$evi2_S_trs_hq <- sapply(1:nrow(all_sites), function(x){
  current_lsp <- all_sites$evi2_S_trs[x] %>% as_date()
  current_site <- all_sites$Location[x]
  current_df <- data %>% filter(Location == current_site)
  current_df_filt <- current_df %>% filter(!is.na(evi2)) %>% filter(abs((date - current_lsp) %>% as.numeric()) <= 5 ) 
  a <- nrow(current_df_filt)
})

all_sites$evi2_D_trs_hq <- sapply(1:nrow(all_sites), function(x){
  current_lsp <- all_sites$evi2_D_trs[x] %>% as_date()
  current_site <- all_sites$Location[x]
  current_df <- data %>% filter(Location == current_site)
  current_df_filt <- current_df %>% filter(!is.na(evi2)) %>% filter(abs((date - current_lsp) %>% as.numeric()) <= 5 ) 
  a <- nrow(current_df_filt)
})


all_sites$G_qual <- sapply(1:nrow(all_sites), function(k){
  if(is.na(all_sites$evi2_G_trs_delta[k])){
    return(NA)
  }
  if(all_sites$evi2_G_trs_hq[k] >= 5){
    return('solid')
  }
  if(all_sites$evi2_G_trs_delta[k] <= 14){
    return('longdash')
  }
  if(all_sites$evi2_G_trs_delta[k] <= 28){
    return('twodash')
  }
  return('dotted')
}) 

all_sites$M_qual <- sapply(1:nrow(all_sites), function(k){
  if(is.na(all_sites$evi2_M_trs_delta[k])){
    return(NA)
  }
  if(all_sites$evi2_M_trs_hq[k] >= 5){
    return('solid')
  }
  if(all_sites$evi2_M_trs_delta[k] <= 14){
    return('longdash')
  }
  if(all_sites$evi2_M_trs_delta[k] <= 28){
    return('twodash')
  }
  return('dotted')
}) 

all_sites$S_qual <- sapply(1:nrow(all_sites), function(k){
  if(is.na(all_sites$evi2_S_trs_delta[k])){
    return(NA)
  }
  if(all_sites$evi2_S_trs_hq[k] >= 5){
    return('solid')
  }
  if(all_sites$evi2_S_trs_delta[k] <= 14){
    return('longdash')
  }
  if(all_sites$evi2_S_trs_delta[k] <= 28){
    return('twodash')
  }
  return('dotted')
}) 

all_sites$D_qual <- sapply(1:nrow(all_sites), function(k){
  if(is.na(all_sites$evi2_D_trs_delta[k])){
    return(NA)
  }
  if(all_sites$evi2_D_trs_hq[k] >= 5){
    return('solid')
  }
  if(all_sites$evi2_D_trs_delta[k] <= 14){
    return('longdash')
  }
  if(all_sites$evi2_D_trs_delta[k] <= 28){
    return('twodash')
  }
  
  return('dotted')
}) 
to_keep <- c('solid' = TRUE,
             'longdash' = TRUE,
             'twodash' = TRUE,
             'dotted' = FALSE)
all_sites$G_keep <- to_keep[all_sites$G_qual]
all_sites$M_keep <- to_keep[all_sites$M_qual]
all_sites$S_keep <- to_keep[all_sites$S_qual]
all_sites$D_keep <- to_keep[all_sites$D_qual]

all_sites$G_keep[is.na(all_sites$G_keep)] <- FALSE
all_sites$M_keep[is.na(all_sites$M_keep)] <- FALSE
all_sites$S_keep[is.na(all_sites$S_keep)] <- FALSE
all_sites$D_keep[is.na(all_sites$D_keep)] <- FALSE


write.csv(all_sites[,c('Location',
                       "evi2_G_trs_delta",
                       "evi2_M_trs_delta",
                       "evi2_S_trs_delta",
                       "evi2_D_trs_delta",
                       "evi2_G_trs_hq",
                       "evi2_M_trs_hq",
                       "evi2_S_trs_hq",
                       "evi2_D_trs_hq",
                       "G_qual",
                       "M_qual",
                       "S_qual",
                       "D_qual",
                       "G_keep",
                       "M_keep",
                       "S_keep",
                       "D_keep")], file = 'all_sites_quality_check_trs_BEFORE.csv')
                       

```
 



```{r}
group_df <- read.csv(here('data/group_cont.csv'))

pdf('pod_pheno_extract_qual_trs.pdf')



for (k in 1:nrow(all_sites)){
  print(k)
  location <- all_sites$Location[k]
  print(location)
  test_site_data <- data %>% filter(Location == location)
  

  vi_pad_col <- 'evi2_pad'
  vi_pad_fitted <-  'evi2_pad_fitted'
    
  g_qual <- all_sites$G_qual[k]
  m_qual <- all_sites$M_qual[k]
  s_qual <- all_sites$S_qual[k]
  d_qual <- all_sites$D_qual[k]
    
  a <- plot_quality(test_site_data,
                     vi_pad_col,
                     vi_pad_fitted,
                     g_qual,
                     m_qual,
                     s_qual,
                     d_qual)
  plot(a[[1]])

  
}




dev.off()


```




