---
title: "Pod work"
author: "Mike Cecil"
date: "2023-07-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Multi-sensor LSP extraction fitting

This script performs the following processing steps
- Rescales variables for use in random forest model
- Creates two random forest models (using S1, S2, VIIRS as input variables and Mark EVI2 as output). 
- The variable inputs are the rough-fit versions of the VI curves, after Whittaker smoothing but before fine-fit Beck smoothing. The variable names are '_pad_fitted' (for Mark) and '_fitted' (for satellite)
- The random forests are created using the ranger package. For each group of sites, the model is trained only on sites not in the current group (to avoid over-fitting)
- This script also calculates mean and median LSP dates based on LSP dates from S1, S2, VIIRS. 

```{r}
library(dplyr)
#library(randomForest)
library(tidyr)
library(ggplot2)
library(stringr)
library(lubridate)
library(Rcpp)
library(phenofit)
library(zoo)
library(here)
library(terra)
library(scorepeak)
library(ranger)
library(pspline)
library(lmodel2)

```


```{r}
fit_var <- function(df, colName, lambda, w_colName = NA, weights = F){
  fitted_vi_col_name <- paste0(colName, "_fitted")
  y_all <- df[[colName]] 
  #  print(y_all)
  y_all[is.infinite(y_all)] <- -9999
  y_all[is.na(y_all)] <- -9999
  if(weights == T ){
    w <- df[[w_colName]]
  } else {
    w <- (y_all != -9999)
  }
  y_whit <- whit2(y_all, lambda, w)
  #  print(y_whit)
  df[[fitted_vi_col_name]] <- y_whit
  return(df)
}

get_bit <- function(number, n) {
  bit <- (number %% 2^(n + 1)) %/% (2^(n))
  return(bit)
}



calculate_Beck_plot_return_dates_rf <- function(df, 
                                                vi_col,
                                                vi_col_fitted,
                                                pred_col,
                                                pred_col_fitted,
                                                mark_lsp_dates,
                                                location){
  
  mark_lsp_dates <- as_date(mark_lsp_dates)
  
  df[['ndvi_pad']] <- df[[vi_col]]
  df[['ndvi_pad_fitted']] <- df[[vi_col_fitted]]

  df[['predict']] <- df[[pred_col]]
  df[['predict_fitted']] <- df[[pred_col_fitted]]
  
  
  max_vi <- max(df$ndvi_pad_fitted, na.rm = T)
  # ## Beck fit
  ndvi_col <- pred_col_fitted
  finefit_mark <- FitDL.Beck(df[[ndvi_col]])
  models_mark <- curvefit(df[[ndvi_col]], methods = 'Beck')
  #dates_indices_mark <- PhenoKl(models_mark$model$Beck, IsPlot = F)
  
  dates_indices_mark_15 <- PhenoTrs(models_mark$model$Beck, IsPlot = F,
                                 trs = c(0.15))
  dates_indices_mark_90 <- PhenoTrs(models_mark$model$Beck, IsPlot = F,
                                 trs = c(0.90))
  dates_indices_mark <- c(dates_indices_mark_15[1], 
                          dates_indices_mark_90[1],
                          dates_indices_mark_90[2],
                          dates_indices_mark_15[2])
  
  
  dates_mark <- df$date[dates_indices_mark]
  dates_collapse_mark <- dates_mark %>% as.character() %>% paste(collapse = ' ')
  ndvi_beck <- finefit_mark$zs$iter2
  df$ndvi_beck <- ndvi_beck
  

  
  
  # colors <- c(`good` = 'green',
  #            `maybe` = 'yellow4',
  #            `no` = 'red')
  
  
 # print(finefit_mark)
#  print(models_mark)
 # print(ndvi_beck)
  p <- ggplot(df) +
  #  geom_point(aes(x = date, y = ndvi_pad), col = 'green') +
  #  geom_point(aes(x = date, y = ndvi_pad), col = 'red', alpha = 0.5) +
    geom_point(aes(x = date, y = ndvi_pad, col = 'red'), alpha = 0.5) +
    geom_line(aes(x = date, y = ndvi_pad_fitted, col = 'red'), alpha = 0.5) +


    geom_point(aes(x = date, y = predict), col = 'blue', alpha = 0.5) +
    geom_line(aes(x = date, y = predict_fitted), col = 'blue', alpha = 0.5) +
    geom_line(aes(x = date, y = ndvi_beck), col = 'grey') + 
    theme_bw() +
    ylim(0, (1.1 * max_vi) ) + 
    ylab(vi_col) +
    geom_vline(xintercept= dates_mark[1], linetype="solid", lwd = 2, color = "lightgreen") +
    geom_vline(xintercept= dates_mark[2], linetype="solid", lwd = 2, color = "darkgreen") +
    geom_vline(xintercept= dates_mark[3], linetype="solid", lwd = 2, color = "yellow2") +
    geom_vline(xintercept= dates_mark[4], linetype="solid", lwd = 2, color = "orange3") +
    geom_vline(xintercept= mark_lsp_dates[1], linetype="dashed", lwd = 2, color = "lightgreen") +
    geom_vline(xintercept= mark_lsp_dates[2], linetype="dashed", lwd = 2, color = "darkgreen") +
    geom_vline(xintercept= mark_lsp_dates[3], linetype="dashed", lwd = 2, color = "yellow2") +
    geom_vline(xintercept= mark_lsp_dates[4], linetype="dashed", lwd = 2, color = "orange3") +
  #  geom_vline(xintercept = maxima_dates, linetype = 'solid', color = 'orange', lwd = 2) +
 #   geom_vline(xintercept = minima_dates, linetype = 'solid', color = 'purple', lwd = 2) +
    
    ggtitle(paste0(location, ' ', dates_collapse_mark))
#  plot(p)
  print(p)
 # return(finefit_mark)
  return(list(p, dates_mark))
  
}

rescaleVect <- function(columnVect){
  columnVect <- as.numeric(columnVect)
  min_vect <- min(columnVect, na.rm = T)
  max_vect <- max(columnVect, na.rm = T)
  transformedVect <- (columnVect - min_vect) * (0.8/(max_vect - min_vect)) + 0.1
}


 
```







```{r}
load(file = here('data/all_sites_post_mgmt.rda'))
load(file = here('data/data_post_VIIRS_sr_fit.rda'))

```



```{r}
## set LSP dates to NA due to quality check

sites_quality_check <- read.csv(here("all_sites_quality_check_trs_AFTER.csv"))
all_sites <- merge(all_sites, 
                   sites_quality_check %>% select(Location, 
                                                  G_keep_post,
                                                  M_keep_post,
                                                  S_keep_post,
                                                  D_keep_post),
                   by = "Location" )

all_sites[all_sites$G_keep_post == FALSE, 'evi2_G_trs'] <- NA
all_sites[all_sites$M_keep_post == FALSE, 'evi2_M_trs'] <- NA
all_sites[all_sites$S_keep_post == FALSE, 'evi2_S_trs'] <- NA
all_sites[all_sites$D_keep_post == FALSE, 'evi2_D_trs'] <- NA

all_sites[all_sites$G_keep_post == FALSE, 'ndvi_G_trs'] <- NA
all_sites[all_sites$M_keep_post == FALSE, 'ndvi_M_trs'] <- NA
all_sites[all_sites$S_keep_post == FALSE, 'ndvi_S_trs'] <- NA
all_sites[all_sites$D_keep_post == FALSE, 'ndvi_D_trs'] <- NA

all_sites[all_sites$G_keep_post == FALSE, 'gcvi_G_trs'] <- NA
all_sites[all_sites$M_keep_post == FALSE, 'gcvi_M_trs'] <- NA
all_sites[all_sites$S_keep_post == FALSE, 'gcvi_S_trs'] <- NA
all_sites[all_sites$D_keep_post == FALSE, 'gcvi_D_trs'] <- NA
```


```{r}

#all_sites <- all_sites %>% distinct()


## Sentinel-1 stopped covering Zambia in 2021-22, so set LSP values to NA
all_sites[grepl('21-22', all_sites$Location), grepl('GEE_s1_', names(all_sites)) ] <- NA


all_sites$start_date_mark <- sapply(1:NROW(all_sites), function(x){
  current_site <- all_sites$Location[x]
  current_df <- data %>% filter(Location == current_site) %>% filter(!is.na(evi2_pad))
  min_date <- min(current_df$date) %>% as.character()
})




## fixing s2 column names for daily data
cont_vct <- all_sites$group_cont
names(cont_vct) <- all_sites$Location

data$group_cont <- cont_vct[data$Location]

s2_cols <- names(data)[substr(names(data), 1, 7) == 'DEA_s2_']
for(s2_col in s2_cols){
  new_col_name <- str_replace(s2_col, 'DEA_s2_', 's2_')
  data[[new_col_name]] <- ifelse(data$group_cont == 'SSA', 
                           as.character(data[[paste0('DEA_', new_col_name)]]),
                           data[[s2_col]])
  data[[new_col_name]] <- data[[new_col_name]] %>% as.numeric()
}





```





```{r}
#rescale variables for use in random forest
mark_bands_to_rescale <- c("ndvi_pad_fitted",
                           "gcvi_pad_fitted" ,
                           "evi2_pad_fitted" )
s1_bands_to_rescale <- c("GEE_s1_A_vh_vv_gf_fitted" ,
                         "GEE_s1_A_rvi_gf_fitted" )
s2_bands_to_rescale_dea <- c("DEA_s2_ndvi_fitted" ,
                             "DEA_s2_gcvi_fitted" ,
                             "DEA_s2_evi2_fitted" )
s2_bands_to_rescale_gee <- c("s2_ndvi_fitted",
                             "s2_gcvi_fitted",
                             "s2_evi2_fitted")

viirs_bands_to_rescale_gee <- c("VIIRS_sr_ndvi_fitted",
                                      "VIIRS_sr_gcvi_fitted",
                                      "VIIRS_sr_savi_fitted",
                                      "VIIRS_sr_evi2_fitted")

#all_sites$s2_source <- NA

rescaled_dfs <- lapply(1:nrow(all_sites), function(k){
  location <- all_sites$Location[k]
  #print(location)
  current_df <- data %>% filter(Location == location)

  
  for(band_to_rescale in c(mark_bands_to_rescale,
                           s1_bands_to_rescale,
                           s2_bands_to_rescale_gee,
                           viirs_bands_to_rescale_gee)){
   # print(band_to_rescale)
    current_df[[paste0(band_to_rescale, "_std")]] <- rescaleVect(current_df[[band_to_rescale]])
  }
  
  current_df <- current_df %>% filter(!is.na(ndvi_pad_fitted))
  
  bands_to_spline <- paste0(c(mark_bands_to_rescale,
                           s1_bands_to_rescale,
                           s2_bands_to_rescale_gee,
                           viirs_bands_to_rescale_gee), '_std')
  for(band_to_spline in bands_to_spline){
    current_df[[paste0(band_to_spline, "_spline")]] <- 10 * predict(sm.spline(current_df$date,
                                       current_df[[band_to_spline]]), 
                             current_df$date, 1) %>% as.numeric()
  }
  return(current_df)
  
  
})


rescaled_dfs_rbind <- do.call('rbind', rescaled_dfs)


 
```







## ranger

```{r}
all_sites$evi2_valid_lsp_count <- sapply(1:nrow(all_sites), function(x){
  l1 <- !(is.na(all_sites$evi2_G_trs[x]))
  l2 <- !(is.na(all_sites$evi2_M_trs[x]))
  l3 <- !(is.na(all_sites$evi2_S_trs[x]))
  l4 <- !(is.na(all_sites$evi2_D_trs[x]))
  l <- l1 + l2 + l3 + l4
})
```



## ranger without spline
```{r}
groups <- all_sites$Group %>% unique()
groups <- groups[groups != 'Zam_21_22']
groups <- groups[groups %in% c("choma" ,
                               "Zam_20_21"  ,    
                               "kenya"  )]
#groups <- groups[groups!= 'planet_stockton']

dep_var <- "evi2_pad_fitted_std"
dep_var_base <- str_replace(dep_var, '_pad_fitted_std', '')

vi_col <- paste0(dep_var_base, '_pad')
vi_col_fitted <- paste0(dep_var_base, '_pad_fitted')
pred_col <- paste0(dep_var_base, '_predict')
pred_col_fitted <- paste0(dep_var_base, '_predict_fitted')

all_sites[[paste0(pred_col, '_G_trs')]] <- NA
all_sites[[paste0(pred_col, '_M_trs')]] <- NA
all_sites[[paste0(pred_col, '_S_trs')]] <- NA
all_sites[[paste0(pred_col, '_D_trs')]] <- NA



indep_var <- c("GEE_s1_A_vh_vv_gf_fitted_std" ,
               "GEE_s1_A_rvi_gf_fitted_std" ,
               "s2_ndvi_fitted_std" ,
               "s2_gcvi_fitted_std"   ,
               "s2_evi2_fitted_std"   ,
               "VIIRS_sr_evi2_fitted_std",
               "VIIRS_sr_gcvi_fitted_std" ,
               "VIIRS_sr_ndvi_fitted_std"  )


sites_bad_lsp <- all_sites[all_sites$evi2_valid_lsp_count < 3, 'Location']

## remove Zambia 21-22 sites from both training and validation
## remove sites with less than 3 valid Mark LSP dates from training only
sites_remove <-  all_sites$Location[grepl('21-22', all_sites$Location)]
sites_bad_lsp <- all_sites[all_sites$evi2_valid_lsp_count < 3, 'Location']
sites_remove_train <- c(sites_remove, sites_bad_lsp)




pdf('rf_plots.pdf')

for(group in groups){
  print(group)
  train_sites <- all_sites %>% filter(Group != group) %>% pull(Location)
  val_sites <- all_sites %>% filter(Group == group) %>% pull(Location)

  train_sites <- train_sites[!(train_sites %in% sites_remove_train)]
  val_sites <- val_sites[!(val_sites %in% sites_remove)]
  
  # print('train sites')
  # print(train_sites)
  # print('val sites')
  # print(val_sites)
  
  train_data <- rescaled_dfs_rbind %>% filter(Location %in% train_sites)
  val_data <- rescaled_dfs_rbind %>% filter(Location %in% val_sites)



  train_data <- train_data[, c(dep_var, indep_var)]
  train_data$dep_var <- train_data[[dep_var]]
  train_data[[dep_var]] <- NULL
  rf <- ranger(dep_var ~ ., data = train_data, write.forest = TRUE)

  val_data$dep_var <- val_data[[dep_var]]
  val_data$dep_var_fitted <- val_data[[paste0(dep_var, '_fitted')]]


  val_data[[paste0(dep_var_base, '_predict')]] <- predict(rf, data = val_data)[['predictions']]
  

  
  for(val_site in val_sites){
    print(val_site)
    current_df <- val_data %>% filter(Location == val_site)
    current_df <- fit_var(current_df, paste0(dep_var_base, '_predict'), lambda = 10000)
    val_site_i <- which(all_sites$Location == val_site)
    mark_lsp_dates <- c(all_sites[[paste0(dep_var_base, '_G_trs')]][val_site_i],
                   all_sites[[paste0(dep_var_base, '_M_trs')]][val_site_i],
                   all_sites[[paste0(dep_var_base, '_S_trs')]][val_site_i],
                   all_sites[[paste0(dep_var_base, '_D_trs')]][val_site_i])
    
    

    
    a <- calculate_Beck_plot_return_dates_rf(current_df, 
                                             vi_col,
                                          vi_col_fitted,
                                          pred_col,
                                          pred_col_fitted,
                                          mark_lsp_dates,
                                          val_site)
    
    
    
    all_sites[[paste0(pred_col, '_G_trs')]][val_site_i] <- a[[2]][1] %>% as.character()
    all_sites[[paste0(pred_col, '_M_trs')]][val_site_i] <- a[[2]][2] %>% as.character()
    all_sites[[paste0(pred_col, '_S_trs')]][val_site_i] <- a[[2]][3] %>% as.character()
    all_sites[[paste0(pred_col, '_D_trs')]][val_site_i] <- a[[2]][4] %>% as.character()
    
  }
}

dev.off()


```



## ranger spline

```{r}
groups <- all_sites$Group %>% unique()
groups <- groups[groups != 'Zam_21_22']
groups <- groups[groups %in% c("choma" ,
                               "Zam_20_21"  ,    
                               "kenya"  )]
#groups <- groups[groups!= 'planet_stockton']

dep_var <- "evi2_pad_fitted_std"
dep_var_base <- str_replace(dep_var, '_pad_fitted_std', '')

vi_col <- paste0(dep_var_base, '_pad')
vi_col_fitted <- paste0(dep_var_base, '_pad_fitted')
pred_col <- paste0(dep_var_base, '_predict')
pred_col_fitted <- paste0(dep_var_base, '_predict_fitted')

all_sites[[paste0(pred_col, '_spline_G_trs')]] <- NA
all_sites[[paste0(pred_col, '_spline_M_trs')]] <- NA
all_sites[[paste0(pred_col, '_spline_S_trs')]] <- NA
all_sites[[paste0(pred_col, '_spline_D_trs')]] <- NA



indep_var <- c("GEE_s1_A_vh_vv_gf_fitted_std" ,
               "GEE_s1_A_rvi_gf_fitted_std" ,
               "s2_ndvi_fitted_std" ,
               "s2_gcvi_fitted_std"   ,
               "s2_evi2_fitted_std"   ,
               "VIIRS_sr_ndvi_fitted_std",
               "VIIRS_sr_gcvi_fitted_std" ,
               "VIIRS_sr_evi2_fitted_std"  )

indep_var_spline <- paste0(indep_var, '_spline')

indep_var <- c(indep_var, 
               indep_var_spline)


## remove Zambia 21-22 sites from both training and validation
## remove sites with less than 3 valid Mark LSP dates from training only
sites_remove <-  all_sites$Location[grepl('21-22', all_sites$Location)]
sites_bad_lsp <- all_sites[all_sites$evi2_valid_lsp_count < 3, 'Location']
sites_remove_train <- c(sites_remove, sites_bad_lsp)




pdf('rf_plots_spline.pdf')

for(group in groups){
  train_sites <- all_sites %>% filter(Group != group) %>% pull(Location)
  val_sites <- all_sites %>% filter(Group == group) %>% pull(Location)
  train_sites <- train_sites[!(train_sites %in% sites_remove_train)]
  val_sites <- val_sites[!(val_sites %in% sites_remove)]
  
  train_data <- rescaled_dfs_rbind %>% filter(Location %in% train_sites)
  val_data <- rescaled_dfs_rbind %>% filter(Location %in% val_sites)



  train_data <- train_data[, c(dep_var, indep_var)]
  train_data$dep_var <- train_data[[dep_var]]
  train_data[[dep_var]] <- NULL
  rf <- ranger(dep_var ~ ., data = train_data, write.forest = TRUE)

  val_data$dep_var <- val_data[[dep_var]]
  val_data$dep_var_fitted <- val_data[[paste0(dep_var, '_fitted')]]


  val_data[[paste0(dep_var_base, '_predict')]] <- predict(rf, data = val_data)[['predictions']]
  

  
  for(val_site in val_sites){
    print(val_site)
    current_df <- val_data %>% filter(Location == val_site)
    current_df <- fit_var(current_df, paste0(dep_var_base, '_predict'), lambda = 10000)
    val_site_i <- which(all_sites$Location == val_site)
    mark_lsp_dates <- c(all_sites[[paste0(dep_var_base, '_G_trs')]][val_site_i],
                   all_sites[[paste0(dep_var_base, '_M_trs')]][val_site_i],
                   all_sites[[paste0(dep_var_base, '_S_trs')]][val_site_i],
                   all_sites[[paste0(dep_var_base, '_D_trs')]][val_site_i])
    
    

    
    a <- calculate_Beck_plot_return_dates_rf(current_df, 
                                             vi_col,
                                          vi_col_fitted,
                                          pred_col,
                                          pred_col_fitted,
                                          mark_lsp_dates,
                                          val_site)
    
    
    
    all_sites[[paste0(pred_col, '_spline_G_trs')]][val_site_i] <- a[[2]][1] %>% as.character()
    all_sites[[paste0(pred_col, '_spline_M_trs')]][val_site_i] <- a[[2]][2] %>% as.character()
    all_sites[[paste0(pred_col, '_spline_S_trs')]][val_site_i] <- a[[2]][3] %>% as.character()
    all_sites[[paste0(pred_col, '_spline_D_trs')]][val_site_i] <- a[[2]][4] %>% as.character()
    
  }
}

dev.off()


```



## satellite mean and median 
```{r}
all_sites$satellite_mean_G_trs <- rowMeans(cbind(as_date(all_sites$DEA_s2_ndvi_G_trs),
                                   as_date(all_sites$DEA_s2_evi2_G_trs),
                                   as_date(all_sites$DEA_s2_gcvi_G_trs),
                                   as_date(all_sites$GEE_s1_A_rvi_gf_G_trs),
                                   as_date(all_sites$GEE_s1_A_vh_vv_gf_G_trs),
                                   as_date(all_sites$VIIRS_sr_ndvi_G_trs),
                                   as_date(all_sites$VIIRS_sr_evi2_G_trs),
                                   as_date(all_sites$VIIRS_sr_gcvi_G_trs)), 
                                   na.rm = T) %>% as_date() 

all_sites$satellite_mean_M_trs <- rowMeans(cbind(as_date(all_sites$DEA_s2_ndvi_M_trs),
                                   as_date(all_sites$DEA_s2_evi2_M_trs),
                                   as_date(all_sites$DEA_s2_gcvi_M_trs),
                                   as_date(all_sites$GEE_s1_A_rvi_gf_M_trs),
                                   as_date(all_sites$GEE_s1_A_vh_vv_gf_M_trs),
                                   as_date(all_sites$VIIRS_sr_ndvi_M_trs),
                                   as_date(all_sites$VIIRS_sr_evi2_M_trs),
                                   as_date(all_sites$VIIRS_sr_gcvi_M_trs)), 
                                   na.rm = T) %>% as_date() 

all_sites$satellite_mean_S_trs <- rowMeans(cbind(as_date(all_sites$DEA_s2_ndvi_S_trs),
                                   as_date(all_sites$DEA_s2_evi2_S_trs),
                                   as_date(all_sites$DEA_s2_gcvi_S_trs),
                                   as_date(all_sites$GEE_s1_A_rvi_gf_S_trs),
                                   as_date(all_sites$GEE_s1_A_vh_vv_gf_S_trs),
                                   as_date(all_sites$VIIRS_sr_ndvi_S_trs),
                                   as_date(all_sites$VIIRS_sr_evi2_S_trs),
                                   as_date(all_sites$VIIRS_sr_gcvi_S_trs)), 
                                   na.rm = T) %>% as_date() 

all_sites$satellite_mean_D_trs <- rowMeans(cbind(as_date(all_sites$DEA_s2_ndvi_D_trs),
                                   as_date(all_sites$DEA_s2_evi2_D_trs),
                                   as_date(all_sites$DEA_s2_gcvi_D_trs),
                                   as_date(all_sites$GEE_s1_A_rvi_gf_D_trs),
                                   as_date(all_sites$GEE_s1_A_vh_vv_gf_D_trs),
                                   as_date(all_sites$VIIRS_sr_ndvi_D_trs),
                                   as_date(all_sites$VIIRS_sr_evi2_D_trs),
                                   as_date(all_sites$VIIRS_sr_gcvi_D_trs)), 
                                   na.rm = T) %>% as_date() 



all_sites$satellite_median_G_trs <- apply(data.frame(as_date(all_sites$DEA_s2_ndvi_G_trs) %>% as.numeric(),
                                   as_date(all_sites$DEA_s2_evi2_G_trs)%>% as.numeric(),
                                   as_date(all_sites$DEA_s2_gcvi_G_trs)%>% as.numeric(),
                                   as_date(all_sites$GEE_s1_A_rvi_gf_G_trs)%>% as.numeric(),
                                   as_date(all_sites$GEE_s1_A_vh_vv_gf_G_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_ndvi_G_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_evi2_G_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_gcvi_G_trs)%>% as.numeric()), 1, median,
                                   na.rm = T) %>% as_date() 

all_sites$satellite_median_M_trs <- apply(data.frame(as_date(all_sites$DEA_s2_ndvi_M_trs) %>% as.numeric(),
                                   as_date(all_sites$DEA_s2_evi2_M_trs)%>% as.numeric(),
                                   as_date(all_sites$DEA_s2_gcvi_M_trs)%>% as.numeric(),
                                   as_date(all_sites$GEE_s1_A_rvi_gf_M_trs)%>% as.numeric(),
                                   as_date(all_sites$GEE_s1_A_vh_vv_gf_M_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_ndvi_M_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_evi2_M_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_gcvi_M_trs)%>% as.numeric()), 1, median,
                                   na.rm = T) %>% as_date() 

all_sites$satellite_median_S_trs <- apply(data.frame(as_date(all_sites$DEA_s2_ndvi_S_trs) %>% as.numeric(),
                                   as_date(all_sites$DEA_s2_evi2_S_trs)%>% as.numeric(),
                                   as_date(all_sites$DEA_s2_gcvi_S_trs)%>% as.numeric(),
                                   as_date(all_sites$GEE_s1_A_rvi_gf_S_trs)%>% as.numeric(),
                                   as_date(all_sites$GEE_s1_A_vh_vv_gf_S_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_ndvi_S_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_evi2_S_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_gcvi_S_trs)%>% as.numeric()), 1, median,
                                   na.rm = T) %>% as_date() 

all_sites$satellite_median_D_trs <- apply(data.frame(as_date(all_sites$DEA_s2_ndvi_D_trs) %>% as.numeric(),
                                   as_date(all_sites$DEA_s2_evi2_D_trs)%>% as.numeric(),
                                   as_date(all_sites$DEA_s2_gcvi_D_trs)%>% as.numeric(),
                                   as_date(all_sites$GEE_s1_A_rvi_gf_D_trs)%>% as.numeric(),
                                   as_date(all_sites$GEE_s1_A_vh_vv_gf_D_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_ndvi_D_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_evi2_D_trs)%>% as.numeric(),
                                   as_date(all_sites$VIIRS_sr_gcvi_D_trs)%>% as.numeric()), 1, median,
                                   na.rm = T) %>% as_date() 
```


```{r}
save(all_sites, file = here('all_sites_post_rf_mean_median.rda'))
save(data, file = here('data_post_rf_mean_median.rda'))
```



